Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-06 gibbs.tex
Update gibbs.tex

\subsection{Implications and future perspectives}
We are aware that the concept introduced in this simulation study need to be experimentally verified.
Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.

\section{Conclusions}
We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited water amount.
We have shown that the compression always decreases the surrounding salinity in the case of strong polyelectrolyte gel.
We have modeled the process of water desalination by sequential combinations of two processes: 
(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity
(2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
We estimated the energy consumtion of this process for production of one liter potable water from brine as $W^{id} =$ 38.2 J/l.
We have shown that this method may compete with the modern technologies used in modern industry. \todo{energy costs of other desalination methods???}

>>>>

\subsection{Implications and future perspectives}
We are aware that the concept introduced in this simulation study need to be experimentally verified.

\section{Conclusions}
We have modeled the compression of the gel in thermodynamic equilibrium with the reservoir of the limited water amount.
We have shown that the compression always decreases the surrounding salinity in the case of strong polyelectrolyte gel.
We have modeled the process of water desalination by sequential combinations of two processes: 
(1) swelling of the gel in \emph{open system}, exchanging ions with a big reservoir at constant salinity
(2) compression of the gel in \emph{closed system}, when the gel affects the salinity in the surrounding solution
We estimated the energy consumtion of the whole process for production of one liter potable water from brine as $W^{id} =$ 38.2 J/l.
Let us compare this value with the energy cost of RO, which is around 20000 J/l.
We have shown that the propsed gel compression method can compete with modern technologies used in modern industry.
